The Eternal Adversary between Censor and Circumvention

### 2024-12-22 paper/paper.tex
Do chores and clean some spell issues

% \usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
% Graphic path
% \graphicspath{{./pics/}}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{orcidlink}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{subcaption}

@@

\subsection{Set Up Proxy Server}
We configure the remote proxy server and the corresponding dependencies since most server sides of the TLS-based protocols require an upstream Web Server to forward unauthorized web traffic, which is always considered an active probe. For more details about how it can be utilised by censor in practice, please refer to section \ref{sec:active_detection}.
To make a TLS-based proxy server work, we must configure the proxy server program, the underlying "fallback" web server, and obtain a SSL certificate. For more about the mechanisms to combat active probing, especially the idea of "fallback", please refer to section \ref{sec:apc}. You can also find the sample configuration file in your repository. %See \ref{sec:config}.
% We publish the notes and more technical details about the servers' configuration processes in the seminar repository.

@@

\subsection{The detection}\label{sec:detection}
Generally speaking, two kinds of approaches try to achieve this goal: passive tests, which try to analyze the existing data and figure out characteristics and patterns that make a disguised traffic identifiable, and active probes, which use measurements such as replay attack, tampering data, and man-in-the-middle attack. We discuss different approaches that try to distinguish "unauthorized" traffic.

\subsection{The Passive Detection}
Passive detection means that the censor analyzes the traffic that goes through their infrastructures (the "Infrastructures" are often gateways but should not be limited to gateways, for example, they can also use optical splitters to intercept traffic from fibers). When people use network tools such as tcpdump or CharlesProxy\texttrademark{} to check traffic, they do almost the same work with the censor, but beyond the idea, the tools that are adopted by censors can sometimes be much more sophisticated. Traffic can be inspected in multiple OSI Layers. Also, different Protocols can be analyzed with different measurements depending on their characteristics (for example, we can analyze a HTTPS traffic with the help of a MITM Attack).

\subsubsection{Effort in decryption}
 The most straightforward way to decide whether a connection is valid is to retrieve the carried payload and censor it. But in the age of AEAD (authenticated encryption with associated data) and HTTPS/SSL, it becomes complicated or can only be partially implemented in a very stringent condition like an attack that utilizes a classical vulnerability Heartbleed \cite{Heartbleed}. In most scenarios, it has been patched.
 \begin{itemize}
    \item  For symmetric-key algorithms, some extremely old encryptions before the advanced encryption standard (AES), such as single DES and RC-4 can be solved in a reasonable time. However, that is not a feasible approach because nowadays, most protocols (both TLS and non-TLS-based) have widely adopted AES algorithms.
    \item There can be more chances when considering the asymmetric-key exchange phases, which only happen when a TLS-based protocol tries to establish. For example, MITM attack, for more detail about MITM, please refer to section \ref{sec:mitm}, which goes on “Active Probing” since it needs to intercept and tamper packets. Shor’s algorithm \cite{Shors_Algorithm} also provides a possibility to solve the question in polynomial time. Still, due to versatile technical limitations, it is generally not practical (such an existing quantum computer’s capability is like "it could tell you there is 70\% chance 15 = $3\times$5").
 \end{itemize}

@@

\begin{figure}[!h]
    \centering
    \input{figures/fallback}
    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
    \label{fig:fallback}
\end{figure}

\subsection{Conclusion}
In conclusion, the central of network censorship circumvention is camouflage or \textbf{collateral freedom}. In practice, both sides, efforts of detection and circumvention use a combination of those techniques. For example, a protocol based on TLS should also consider its packet length characteristics. There are still some topics and remarkable technologies I cannot cover, such as identifying protocols with Deep Packet Inspection (DPI) in multiple OSI Layers and machine learning. I thought domain fronting used to be an outstanding idea which is one of the best practices of the idea.
TOR provided domain fronting \cite{domainfronting} based meek bridge \cite{meek} before. Due to various factors such as this technology can also be abused to perform stealthy internet attacks, most CDN providers stopped the support. It also exhibits some temporal characteristics. Internet freedom is a significant topic, and though we focus on the technical details in this paper, we should recognize that it needs a collective effort to defend freedom, as it is a citizen's right that cannot be deprived.

@@

\bibliography{ref}

\appendix
\section{Setting Up Proxy Server}
In this appendix, we will elaborate on some technical details about our methodology.

@@

\subsection{Configuration}\label{sec:config}
We made the sample configuration files available in folder \texttt{resources/config}. For more details, please refer to those projects' documents and the Linux man page or send an email to me.

\appendix
\section{Data Collection and Analysis}
We have published the support code and put it in folder \texttt{resources/Code} at the same project. The manual can also be found in \texttt{resources/Manual}.

>>>>

% \usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
% Graphic path
% \graphicspath{{./pics/}}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{orcidlink}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

@@

\subsection{Set Up Proxy Server}
We configure the remote proxy server and the corresponding dependencies since most server sides of the TLS-based protocols require an upstream Web Server to forward unauthorized web traffic, which is always considered an active probe. For more details about how it can be utilized by censor in practice, please refer to section \ref{sec:active_detection}.
To make a TLS-based proxy server work, we must configure the proxy server program, the underlying "fallback" web server, and obtain a SSL certificate. For more about the mechanisms to combat active probing, especially the idea of "fallback", please refer to section \ref{sec:apc}. You can also find the sample configuration file in your repository. %See \ref{sec:config}.
% We publish the notes and more technical details about the servers' configuration processes in the seminar repository.

@@

\subsection{The detection}\label{sec:detection}
Generally speaking, two kinds of approaches try to achieve this goal: passive tests, which try to analyze the existing data and figure out characteristics and patterns that make a disguised traffic identifiable, and active probes, which use measurements such as replay attack, tampering data, and man-in-the-middle attack. We discuss different approaches that try to distinguish unauthorized traffic.

\subsection{The Passive Detection}
Passive detection means that the censor analyzes the traffic that goes through their infrastructures (the Infrastructures are often gateways but should not be limited to gateways, for example, they can also use optical splitters to intercept traffic from fibers). When people use network tools such as tcpdump or CharlesProxy\texttrademark{} to check traffic, they do almost the same work with the censor, but beyond the idea, the tools that are adopted by censors can sometimes be much more sophisticated. Traffic can be inspected in multiple OSI Layers. Also, different Protocols can be analyzed with different measurements depending on their characteristics (for example, we can analyze a HTTPS traffic with the help of a MITM Attack).

\subsubsection{Effort in decryption}
 The most straightforward way to decide whether a connection is valid is to retrieve the carried payload and censor it. But in the age of AEAD (authenticated encryption with associated data) and HTTPS/SSL, it becomes complicated or can only be partially implemented in a very stringent condition like an attack that utilizes a classical vulnerability Heartbleed \cite{Heartbleed}. In most scenarios, it has been patched. 
 \begin{itemize}
    \item  For symmetric-key algorithms, some extremely old encryptions before the advanced encryption standard (AES), such as single DES and RC-4 can be solved in a reasonable time. However, that is not a feasible approach because nowadays, most protocols (both TLS and non-TLS-based) have widely adopted AES algorithms.
    \item There can be more chances when considering the asymmetric-key exchange phases, which only happen when a TLS-based protocol tries to establish. For example, MITM attack, for more detail about MITM, please refer to section \ref{sec:mitm}, which goes on Active Probing since it needs to intercept and tamper packets. Shor’s algorithm \cite{Shors_Algorithm} also provides a possibility to solve the question in polynomial time. Still, due to versatile technical limitations, it is generally not practical (such an existing quantum computer’s capability is like "it could tell you there is 70\% chance 15 = $3\times$5").
 \end{itemize}

@@

\begin{figure}[!h]
    \centering
    \input{include/fallback}
    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
    \label{fig:fallback}
\end{figure}

\subsection{Conclusion}
In conclusion, the central of network censorship circumvention is camouflage or \textbf{collateral freedom}. In practice, both sides, efforts of detection and circumvention use a combination of those techniques. For example, a protocol based on TLS should also consider its packet length characteristics. There are still some topics and remarkable technologies I cannot cover, such as identifying protocols with Deep Packet Inspection (DPI) in multiple OSI Layers and machine learning. Domain fronting \cite{domainfronting} used to be an outstanding idea which is one of the best practices of the idea. 
TOR provided domain-fronting-based meek bridge \cite{meek} before. Due to various factors, such as the fact that this technology can also be abused to perform stealthy internet attacks, most CDN providers stopped the support. It also exhibits some temporal characteristics. Internet freedom is a significant topic, and though we focus on the technical details in this paper, we should recognize that it needs a collective effort to defend freedom, as it is a citizen's right that cannot be deprived.

@@

\bibliography{paper}

\appendix
\section{Setting Up Proxy Server}
In this appendix, we elaborate on some technical details about our methodology.

@@

\subsection{Configuration}\label{sec:config}
We make the sample configuration files available in folder \texttt{resources/config}. For more details, please refer to those projects' documents and the Linux man page or send an email to me.

\appendix
\section{Data Collection and Analysis}
We publish the support code and put it in folder \texttt{resources/Code} at the same project. The manual can also be found in \texttt{resources/Manual}.
